A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Long comment on coverage and reduction
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1061 43ef1190-90fd-4dd7-a769-d0121f02b80e

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN, which is also used to manage the datasets
in the ``LOD cloud'')\todo{expand on the coverage}, as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in the companion technical report
\cite{kjernsmo_add_survey_2015}.% Appendix~\ref{app:reduction}.
\todo{more detail on filtering}

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider detailed in the companion technical report
\cite{kjernsmo_add_survey_2015}, resulting in 7745 requests, done on
2015-01-02. Although this is not a very large number, we assume that
caching headers are usually set on a per-host basis, if any
differences exist, they are likely on different types, and so the
number of hosts is more important than the number of resources.

@@

>>>>

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN), as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in the companion technical report
\cite{kjernsmo_add_survey_2015}.% Appendix~\ref{app:reduction}.

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider detailed in the companion technical report
\cite{kjernsmo_add_survey_2015}, resulting in 7745 requests, done on
2015-01-02.

@@

A key challenge to the validity of the survey is biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples in the crawl is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represent the breadth of the Semantic Web, momentarily at least.

As for the coverage of vocabularies, we realize that LODstats might
have been a better source, but we have been able to select the most
important, and not far inferior in number. The number of SPARQL
endpoints found in SPARQLES is larger than LODstats, and we also
looked for further endpoints both in the BTC2014 and our own crawl,
finding only a few. If endpoints went underdiscovered, then there is a
discovery problem that is beyond this survey to rectify.

The data reduction that was subsequently done was mainly done to
eliminate errors. We have not investigated biases that may be
introduced by discarding momentarily dysfunctional parts of the
Semantic Web, but we investigated whether the freshness lifetimes
reported in the case of certain errors were distributed differently
from those that returned a valid response, the companion technical
report \cite{kjernsmo_add_survey_2015}. We found that they were, but
we have assumed that this is due to that errors are configured to be
cached differently, which we know from experience is common
practice. The following analysis is based on valid responses.
